---
title: "cellScaleFactors"
author: "Sean Maden"
date: "2023-09-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The `cellScaleFactors` package provides access to cell size scale factor values 
from the literature. These are useful for cell type reference normalization on
type-specific cell sizes prior to performing bulk transcriptomics deconvolution.

# Installation

Install and load the most recent version of this package with:

```{r}
if(!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("cellScaleFactors")

# load
library(cellScaleFactors)
```

# Get data from the hubs

Retrieve the cell scale factors datasets from the hubs with the following.

```{r, eval = F}
libv <- c("AnnotationHub", "ExperimentHub")
sapply(libv, library, character.only = T)

# connect to the hubs
cache.path <- tools::R_user_dir("cellScaleFactors")
setExperimentHubOption("CACHE", cache.path)
hub <- ExperimentHub::ExperimentHub()                    

# query for the cell scale factors table
rmdat <- AnnotationHub::query(hub, "cellScaleFactors") # query the hubs
```

# Session info

```{r}
sessionInfo()
```
